---
title: "Structured Abstract"
author: "Yang Cong"
date: "2022/1/20"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(fig.align = "center")
```

```{r load, include=FALSE}
# Source the code from analysis script in src folder
 library('ProjectTemplate')
 library(hms)
 library(dplyr)
 library(tidyr)
 library(ggplot2)
 load.project()
 source("src/eda.R")
```
# **Context**
#### The dataset given is created from application checkpoint and system metric output from the production of a terapixel image. By analysing it we can have a better understanding of the server so that we can improve it in details in the future.

# **Objective**
####  The project need us to analyse the data to evaluate the perfpormance of Terapixel rendering in Cloud (Super)computing. In this project I studied the relationship between the various data and evaluated the performance and efficiency of each cpu.

# **Method**
#### I focus entirely on the EDA process. I use R to clean, organize and analyze this data, use templates to ensure that the project can be reused, and use git for version control.

# **Results**
#### I managed to discover the connection between the sets of data, understand the relationship between efficiency and performance, and give a way to identify the efficiency of a particular gpu. For example, find the event dominates task runtimes.
```{r echo=FALSE}
barplot(height = y_duration,
        names.arg = x_duration,
        col = 'orange',
        border = '#ffffff')
```
#### And list the slowest GPU.
```{r echo=FALSE}
ggplot(host_card, aes(y=Total_Render_time_avg, x=c_card, fill =  c_card))+
  geom_boxplot() + ggtitle("Event Names Run Time")+scale_x_discrete(guide = guide_axis(n.dodge=3))+
  theme(plot.title = element_text(hjust = 0.05))
```
# **Novelty**
#### Unlike some of my previous predecessors' work results, I only focused on the EDA process. This may not be comprehensive, but it is possible to get a proper understanding of it.